Robotic Cart System

### 2021-04-07 parts/20-system_architecture.tex
Create 20-system_architecture.tex
Update 20-system_architecture.tex

%======================================================================
\chapter{Introduction}
\label{ch: Chapter1}
%======================================================================

%----------------------------------------------------------------------
\section{Problem Statement}
%----------------------------------------------------------------------
Helicopters are of a paramount importance as
they are used in many civilian and military applications due to their ability for vertical take-off and landing. To enable their use in such applications, intensive research has been conducted to date since helicopters involve complex nonlinear dynamics. Most of the work on helicopter based research requires dedicated computers for controlling their motion to specific configurations and resistant to turbulent conditions. Such methods are expensive and time-consuming to develop. Implementation of motion control techniques using cost-effective hardware is still a challenge.

In this project, we are proposing an algorithm for smart control of a team of two degree-of freedom (two-DOF) helicopters using conventional motion control in cooperation with machine learning techniques where a user will be able to configure helicopters from any initial position. Even though conventional techniques have been tested with simple platforms in the literature, the current project employs conventional motion control strategies in cooperation with machine learning technique (reinforcement learning, for instance) for a team of helicopters as well as introducing user control via mobile devices. This project is expected to encourage research in this area as well as serve as an educational tool in teaching environments.

%----------------------------------------------------------------------
\section{Literature Review}
%----------------------------------------------------------------------
Our project requires a great deal of research as some of our tasks have not been attempted before.  As a result, we have examined research papers, work complete by other projects at Bradley University, and documentation/teaching materials from Quanser Inc.

Among the major challenges in developing unmanned systems is to implement a modular, cost-effective, and robust teleoperation system, where the motion of a group of helicopters is controlled by mobile devices. In some cases, computer simulations are conducted to reveal the performance control structures of a 2-DOF helicopter~\cite{DArpino2010}. A large body of research has been conducted in the literature to focus on developing different control structures, such as linear-quadratic regulators (LQR)/Gaussian (LQG), sliding-mode controls (SMC), and advance nonlinear controls, that are specifically applied to 2-DOF helicopters. See~\cite{Subramanian2016-Robust,Ahmed2010-Sliding}, for example, and some references therein. Furthermore,  soft-computing tools, such as fuzzy-logic, neural networks, and a few combinations of them are employed for controlling the motion of a 2-DOF helicopter~\cite{Chang2017-Fuzzy,Kayacan2016-Fuzzy,Gao2016-DataDriven,Hernandez2012-Decentralized}.

The documentation of Quanser AERO\footnote{See \href{https://www.quanser.com/}{https://www.quanser.com/} for details} employs LQR and LQG motion control techniques for teaching purposes.  This involves creating a linearized system model to calculate the LQR state-feedback gain.  A model reference adaptive control (MARC) scheme using Lyapunov functions has been used by~\cite{Subramanian2016-Robust} for adaptive motion control of a 2-DOF helicopter.  SMC is a nonlinear control technique to drive the system states onto a surface in the state space.  This method has been used  by~\cite{Ahmed2010-Sliding}.  Fuzzy-logic controllers use an inference engine to produce an output as used in~\cite{Chang2017-Fuzzy,Kayacan2016-Fuzzy}.  The ADP technique does not rely on knowledge of the system model.  Instead, it uses data to reconstruct the states as preformed by~\cite{Gao2016-DataDriven}.  Authors in~\cite{Hernandez2012-Decentralized} used high order neural networks (HONN) to approximate non-linearities in the system model.

As can be noticed, most of the motion control techniques are either tested using computer simulations or use dedicated computational platforms, that may not be modular and/or cost-effective, for developing motion control algorithms. This is due to the fact that the aforementioned techniques are mainly to propose novel motion control techniques and not focused on hardware implementation platforms. Therefore, the current work considers implementing a conventional motion control technique using modular and cost-effective hardware platforms in the context of a teleoperation system, where a human operator has the ability to control the motion of a team of helicopters using a smart mobile device.

%----------------------------------------------------------------------
\section{Report Organization}
%----------------------------------------------------------------------
This report is organised into 6 chapters.  Chapter \ref{ch: Chapter1} discusses what this project hopes to accomplish and what similar projects have completed.  Chapter \ref{ch: Chapter2} explains how to create a mathematical model for the system.  Chapter \ref{ch: Chapter3} provides a breif explanation of the control algorithms and architectures used.  Chapter \ref{ch: Chapter4} contains the results from our simulations.  Chapter \ref{ch: Chapter5} disucsses results from USB, Raspberry Pi, and Mobile Device implementation.  Chapter \ref{ch: Chapter6} concludes the paper and provides insight into future directions.

>>>>

%======================================================================
\chapter{System Architecture}
\label{ch: Chapter2}
%======================================================================

%----------------------------------------------------------------------
\section{System Block Diagram}
%----------------------------------------------------------------------
The overall system architecture of this project consists of two subsystems which are the Mobile Cart and the Remote Target, which is held by the user or customer, as shown in \autoref{fig:sys_block_diag}. The proposed smart robotic cart is a wheeled robot that sends and receives radio signals to follow the remote target which acts as the beacon for the robotic cart system.

\vspace*{12pt}
\noindent

The high-level system block diagram of the proposed robotic cart (prototype) is shown in \autoref{fig:sys_block_diag}. There are four inputs to the proposed cart system. The robotic cart is supplied power through a battery that is mounted in the chassis of the robotic cart. There will be an on/off switch to allow the system to be powered down when not in use. The motion of the cart is dependent on the motion of the remote. A stretch goal for the project are mode selection buttons that allow the user to put the robotic cart system into different operating modes.

\vspace*{12pt}
\noindent

The main output of the system is the position trajectory of the robotic cart in its environment. When the user moves with the remote, the cart is designed to follow the user. The other output of the robotic cart system is a status indication in the form of LED lights. These lights will be used to notify the user of the status of the robotic cart.

\begin{figure}[!h]
    \centering
    \includegraphics[scale=0.9]{figs/system_block_diagram_2}
    \caption{System level block diagram detailing inputs and outputs to the
      mobile cart system.}
	\label{fig:sys_block_diag}
\end{figure}

%----------------------------------------------------------------------
\section{Subsystem Block Diagrams}
%----------------------------------------------------------------------
The Mobile Cart and the Remote Target subsystems are two separate operations within the robotic cart system that run simultaneously. The two subsystems communicate with one another by relaying radio messages between them. The first block diagram is of the Remote Target subsystem shown in \autoref{fig:remote_block_diag}. Of the two subsystems the Remote Target is the simplest since it only requires an XBee module attached to a 7.4 volt Li-Po battery with a voltage regulation circuit since the XBee has a smaller input voltage of 3.3 volts.

\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.9]{figs/remote_target_block_diagram}
  \caption{Remote Target block diagram}
  \label{fig:remote_block_diag}
\end{figure}

\vspace*{12pt}
\noindent
The Mobile Cart subsystem block diagram is shown in \autoref{fig:mobile_block_diag}. The cart requires a power source, which will be a Li-Po battery since the Li-Po works well with powering the embedded computer (BeagleBone Blue). The power to the subsystem will be toggled by an on/off switch located on the chassis of the robotic cart. The mode selection buttons for changing the operating mode of the robotic cart is a stretch goal of the project and will be implemented on the cart if we have time. The final input to the mobile cart subsystem is the XBee network messages received from the remote target.

\vspace*{12pt}
\noindent
There are three outputs of the mobile cart subsystem. The first is the wheel velocities that move the cart. There will also be LEDs to indicate the status of the system to the user. Lastly, the cart will send radio messages to the remote target by means of a parabolic array of XBee radio modules.

\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.82]{figs/mobile_cart_block_diagram}
  \caption{Block diagram showing the subsystem-level components of the proposed robotic cart.}
  \label{fig:mobile_block_diag}
\end{figure}

%----------------------------------------------------------------------
\section{System Components}
%----------------------------------------------------------------------
There are several components that are required for the mobile cart system. Although some of these parts are available in the Bradley University laboratory, other parts must be purchased. The parts that exist in the lab are shown in \autoref{tab:Partslablist}. Also, \autoref{tab:Partslist} shows the list of parts that we must purchase. The parts lists shown are the parts needed to build two mobile cart systems.

\begin{table}[h!]
  \centering
  \begin{tabular}{c|c}
      \toprule
      \textbf{Quantity} & \textbf{Parts}\\
      \toprule
      2 & Budget Bot Chassis\\
      4 & 10 uF Ceramic Capacitor\\
      4 & LM1117 Regulator\\
      2 & Battery Packs for Budget Bot\\
      8 & 9V Batteries\\
      4 & Solderable PCB Boards\\
      3 & XBee USB Adapter\\
      \bottomrule
      %\multicolumn{2}{r|}{\textbf{Total}} & \$ 562.34\\
      %\bottomrule
  \end{tabular}
  \caption{Parts Available in Laboratory}
  \label{tab:Partslablist}
\end{table}

\begin{table}[h!]
  \centering
  \begin{tabular}{c|c|c}
    \toprule
    \textbf{Quantity} & \textbf{Parts} & \textbf{Price}\\
    \toprule
    4 & Pololu 37D Metal Gear motor 4751 & \$ 39.95\\
    12 & XBee S2C Module & \$ 23.10\\
    10 & XBee Adapter Board & \$ 4.99\\
    2 & Twotrees 4 Lead Nema 17 Stepper Motor & \$ 9.99\\
    1 & 4-Pin JST SH Connector - 20 Pack & \$ 7.99\\
    1 & 6-Pin JST SH Connector - 10 Pack & \$ 9.99\\
    1 & Aluminum Foil Tape - 2 in x 5 yd & \$ 6.05\\
    \bottomrule
    \multicolumn{2}{r|}{\textbf{Total}} & \$ 562.34\\
    \bottomrule
  \end{tabular}
  \caption{Purchased parts for the Robotic Cart Project}
  \label{tab:Partslist}
\end{table}

\vspace*{12pt}
\noindent
The main components for this project are the Budget Bot Chassis (\autoref{fig:budgetBotChassis}), the BeagleBone Blue embedded computer (\autoref{fig:beagleboneBlue}), and the XBee S2C Modules (\autoref{fig:XBeeModule}). Another major component is the reflector array that
will be used to directionalize the RF signals received from the remote target that is with the user.

\begin{figure}
  \centering
  \begin{minipage}[t]{0.32\textwidth}
    \includegraphics[width=1\textwidth]{figs/img/budgetbot_chassis}
    \captionsetup{width=\textwidth}
    \caption{Budget Bot Chassis}
    \label{fig:budgetBotChassis}
  \end{minipage}%
  \begin{minipage}[t]{0.32\textwidth}
    \includegraphics[width=1\textwidth]{figs/img/beaglebone_blue}
    \captionsetup{width=\textwidth}
    \caption{BeagleBone Blue}
    \label{fig:beagleboneBlue}
  \end{minipage}
  \begin{minipage}[t]{0.32\textwidth}
    \includegraphics[width=1\textwidth]{figs/img/Xbee-S2C-Module}
    \captionsetup{width=\textwidth}
    \caption{XBee S2C Module}
    \label{fig:XBeeModule}
  \end{minipage}
\end{figure}

\vspace*{12pt}
\noindent
The reflector array will be mounted on top of the cart where it will be attached with a stepper motor. There are two reflector designs that we will be evaluating in this project. The first, shown in \autoref{fig:parabolodialReflector}, is a paraboloidal reflector which maximizes the signal strength of signals that come into the reflector directly perpendicularly. Since the remote will be carried by the user, it is likely that it will be positioned at a higher altitude than the reflector array. The paraboloidal reflector design may not be able to pick up the signals from the remote as well because of this. To solve this problem, we designed a combination parabolic/paraboloidal reflector, as shown in \autoref{fig:parabolicReflector}. The lower half of this reflector is paraboloidal in shape to limit the signals coming from below. The upper part of the reflector is strictly parabolic. This shape focuses the signals in the horizontal plane, but allows signals from above to still be received. We plan to construct both of these reflector designs by 3d printing the frames, then lining them with reflective foil tape. Both models will then be tested to determine which design works better.

\begin{figure}[h!]
  \centering
  \begin{minipage}[t]{0.5\textwidth}
    \centering
    \includegraphics[height=2in]{figs/img/paraboloidalReflector}
    \captionsetup{width=\textwidth, justification=raggedright}
    \caption{Paraboloidal Reflector Model}
    \label{fig:parabolodialReflector}
  \end{minipage}
  \begin{minipage}[t]{0.4\textwidth}
    \centering
    \includegraphics[height=2in]{figs/img/parabolicReflector}
    \captionsetup{width=\textwidth, justification=raggedright}
    \caption{Combined Parabolic/Paraboloidal Reflector}
    \label{fig:parabolicReflector}
  \end{minipage}
\end{figure}

\subsection{Operation of Mobile Cart System}
The Mobile Cart will controlled by a central embedded computer which we are using the BeagleBone Blue for. Two DC motors will be used to drive wheels to move the cart. Five XBee modules will be used to allow communication with the remote target. One of these radio sensors will be mounted on top of the cart to broadcast in all directions. The other four sensors will be placed inside parabolic reflectors at right angles to each other. This sensor array will be mounted on a stepper motor to allow rotation.
